Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex
pass on conclusions

Several approaches have been proposed in the literature to reduce debugging
costs through automated software fault diagnosis with the goal of
improving productivity in software developement. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis
techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).

>>>>

Several approaches have been proposed in the literature to reduce
software debugging costs through automated fault diagnosis with the
goal of improving productivity in software development. In this
domain, Dynamic Slicing (\ds) and Spectrum-based Fault Localization
(\sfl) are very popular techniques and normally seen as complementary.

This paper reports the outcome of a comprehensive study using
real-world applications with the goal of demystifying the impact of
combining \ds~with \sfl. The results of our empirical study show that,
in practice, \ds\ misses faulty statements infrequently $9\%$ ($23$
misses in $260$ cases) and that the \ds-\sfl~combination, coined as
\combpar{k}, improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$
on average).
